---
title: "Homework 6"
author: Sanjana Batabyal 
output: github_document
---

This is my solution to Homework 6.

```{r setup}
library(tidyverse)
library(magrittr)
library(modelr)
library(mgcv)
```

## Problem 1
Manipulating the dataset to our preferences. Creating a city_state variable. Creating a binary resolution variable. Removing cities that do not report race from dataset.
```{r, echo=FALSE, include=FALSE}
homicide=
  read_csv("data/homicide-data.csv", na=c("", "NA", "Unknown")) %>%
  mutate(city_state=str_c(city, state, sep="_"),
         victim_age=as.numeric(victim_age),
    resolution=case_when(
    disposition=="Closed without arrest" ~ 0,
    disposition=="Closed by arrest" ~ 1,
    disposition=="Open/No arrest" ~ 0)) %>%
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa_AL", 
    city_state != "Dallas_TX",
    city_state != "Phoenix_AZ",
    city_state != "Kansas City_MO") %>%
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```
Focusing on the city of Baltimore, MD.
```{r, echo=FALSE}
baltimore=
  homicide %>% filter(city_state=="Baltimore_MD")

glm(resolution ~ victim_age + victim_race + victim_sex,
    data=baltimore,
    family=binomial()) %>%
  broom::tidy() %>%
  mutate(
    OR=exp(estimate),
    CI_lower=exp(estimate)-1.96*std.error,
    CI_upper=exp(estimate)+1.96*std.error
  ) %>%
  select(term, OR, starts_with("CI")) %>%
  knitr::kable(digits=3)
```
Applying this across all the remaining cities in the dataset.
```{r, echo=FALSE}
hom_results=
homicide %>%
  nest(data = -city_state) %>%
  mutate(
    models=
      map(.x=data, 
          ~glm(resolution ~ victim_age + victim_race + victim_sex,
          data=.x,
          family=binomial())),
    results=map(models, broom::tidy)
  ) %>%
  select(city_state, results) %>%
  unnest(results) %>%
   mutate(
    OR=exp(estimate),
    CI_lower=exp(estimate)-1.96*std.error,
    CI_upper=exp(estimate)+1.96*std.error
  ) %>%
  select(term, OR, starts_with("CI"))
```
Creating a plot of hom_results.
```{r, echo=FALSE}
hom_results %>%
  filter(term == "victim_sexMale") %>%
  mutate(city_state = fct_reorder(city_state, OR)) %>%
  ggplot(aes(x=city_state, y=OR)) +
  geom_point() +
  geom_errorbar(aes(ymin=CI_lower, ymax=CI_upper)) +
  theme(axis.text.x=element_text(angle=90, hjust=1))
```
## Problem 2
Loading and cleaning the data for regression analysis.
```{r, echo=FALSE, include=FALSE}
birthweight=
  read_csv("data/birthweight.csv")
```
Proposing a regression model for birthweight. For my own model I will be seeing the effect of mother's weight at birth, mother's age at birth, and mother's height.
```{r, echo=FALSE}
birthweight_m1=
 lm(bwt ~ delwt + mheight + momage + mheight*delwt + momage*delwt + momage*mheight + delwt*mheight*momage,
    data=birthweight)

summary(birthweight_m1)
broom::glance(birthweight_m1)
broom::tidy(birthweight_m1)

par(mfrow=c(2,2))
plot(birthweight_m1)
```
Creating a regression model using length at birth and gestational age as predictors (main effects only).
```{r, echo=FALSE}
birthweight_m2=
 lm(bwt ~ blength + gaweeks,
    data=birthweight)

summary(birthweight_m2)
broom::glance(birthweight_m2)
broom::tidy(birthweight_m2)

par(mfrow=c(2,2))
plot(birthweight_m2)
```
Creating a regression model using head circumference, length, sex, and all interactions (including the three-way interaction) between these.
```{r,echo=FALSE}
birthweight_m3=
 lm(bwt ~ bhead + blength+ babysex + bhead*blength + bhead*babysex +
      blength*babysex + bhead*blength*babysex,
    data=birthweight)

summary(birthweight_m3)
broom::glance(birthweight_m3)
broom::tidy(birthweight_m3)

par(mfrow=c(2,2))
plot(birthweight_m3)
```
Comparing the models, we will be evaluating the models by the AICs. The most desirable model will have the lowest AIC. Our first model, looking at mother's age, height, and weight, has an AIC of 66030.46. The second model, looking at birth length and gestational age has an AIC of 62770.64. The third model, looking at head circumference, length, and sex, has an 61501.19. Looking at all of these AIC values, the third model has the lowest AIC value leading me to conclude that the third model is preferred.  

##Problem 3